Presentation Title

### 2017-08-04 thesis/chapters/ch1-intro.tex
Write abstract

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
We call our protocol ``Checkpoint Consensus''.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain consensus protocol---Checkpoint Consensus.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse Checkpoint Consensus to ensure correctness as defined in our architecture.
    \item We implement Checkpiont Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

>>>>

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
We call our protocol CheckpointConsensys.
% TODO mention consensus and trade off?

Our main contributions are the following.
\begin{itemize}
    \item We formally introduce a blockchain system---CheckpointConsensys.
        It uses individual hash chains and checkpoints on every node to achieve
        horizontally scalable for the first time.
    \item We formally analyse CheckpointConsensys to ensure correctness as defined in our architecture.
    \item We implement Checkpiont Consensus with experiment with up to 1200 nodes,
        our results show strong evidence of horizontal scalability.
\end{itemize}

### 2017-08-04 thesis/chapters/ch3-model.tex
Write abstract

Our system---Checkpoint Consensus consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interact with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

@@

\section{System overview}
\label{sec:system-overview}
The Checkpoint Consensus architecture is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consist of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronisation happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

>>>>

Our system---CheckpointConsensys consist of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interact with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

@@

\section{System overview}
\label{sec:system-overview}
The architecture is visualised in~\Cref{fig:architecture}.
\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{architecture}
\caption{Overview of the system architecture}
\label{fig:architecture}
\end{figure}
It consist of one data structure---Extended TrustChain, and three protocols.
The protocols have distinct roles which are evident from their names.
They run concurrently and do not interact with each other.
The only synchronisation happens on the Extended TrustChain layer, where all the protocols read and write from it.
We first describe each component individually, starting with Extended TrustChain, and then explain how they fit together.

### 2017-08-04 thesis/formalities/abstract.tex
New intro and etc.
Write synchroniser
Edit ch1 and ch2
Refactor validation protocol
Write abstract

\noindent \textbf{Author}\\
\begin{tabular}{l}
TODO AUTHOR\\
\\
\end{tabular}\\
\noindent \textbf{Title}\\
\begin{tabular}{l}
TODO TITLE\\
\\
\end{tabular}\\
\noindent \textbf{MSc presentation}\\
\begin{tabular}{l}
% <MM> DD, YYYY (like \today)
TODO GRADUATION DATE\\
\\
\end{tabular}

@@

\noindent \textbf{Graduation Committee}\\
\begin{tabular}{ll}
TODO GRADUATION COMMITTEE & Delft University of Technology \\
% The order of listing the names: Graduation prof, supervisor(s), others ordered by title + alphabetical
%examples:
%prof. dr. ir. H. J. Sips (chair) & Delft University of Technology \\
%ir. dr. D. H. J. Epema           & Delft University of Technology \\
\end{tabular}

\begin{abstract} %de abstract bevat alleen een korte samenvatting van de inhoud van het onderzoek
TODO ABSTRACT
\end{abstract}

>>>>

\noindent \textbf{Author}\\
\begin{tabular}{l}
Kelong Cong\\
\\
\end{tabular}\\
\noindent \textbf{Title}\\
\begin{tabular}{l}
Blockchain Consensus Protocol with Horizontal Scalability\\
\\
\end{tabular}\\
\noindent \textbf{MSc presentation}\\
\begin{tabular}{l}
% <MM> DD, YYYY (like \today)
31st August 2017\\
\\
\end{tabular}

@@

\noindent \textbf{Graduation Committee}\\
\begin{tabular}{ll}
% The order of listing the names: Graduation prof, supervisor(s), others ordered by title + alphabetical
%examples:
Prof. dr. ir. D. H. J. Epema            & Delft University of Technology \\
Dr. ir. J. A. Pouwelse                  & Delft University of Technology \\
Dr. Z. Erkin                            & Delft University of Technology \\
\end{tabular}

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised system.
However, scalability remains a key challenge.
Without a horizontally scalable solution, blockchain system remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system which we call CheckpointConsensys.
Each node in our system maintain individual hash chains,
which only stores transactions that involve the node.
Consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the individual hash chains,
thus a single checkpoint block may represent a large set of transaction blocks.
The consensus protocol does not imply transaction validity.
Hence we include a validation protocol which allows nodes to verify that the counterparty correctly recorded the transaction.
% how good is the solution?
We implement a CheckpointConsensys prototype and evaluate it experimentally.
Our results show strong indication of horizontal scalability even in the worst case,
where every transaction is with a randomly selected node.
For 1200 nodes, we were able to perform almost 5000 transactions per second,
orders of magnitude higher than the 7 transaction per second limit of Bitcoin.
\end{abstract}
